---
title: "ANOVA"
author: "Steve Mansfield"
date: "04/09/2023"
output:
  xaringan::moon_reader:
    css: xaringan-themer.css
    self_contained: true
    lib_dir: libs
    nature:
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
      ratio: 16:9
---
<style type="text/css">
.smaller { font-size: 90%}
table { font-size: 80%}
td { padding: 0ex}
</style>
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
options(htmltools.dir.version = FALSE)
options(scipen = 1, digits = 4)

library(tidyverse)
library(kableExtra)
xaringanExtra::use_xaringan_extra(c("tile_view","scribble","panelset"))

library(xaringanthemer)
library(gridExtra)
style_mono_accent(
  base_color = "#1c5253",
  base_font_size = "25px",
  header_font_google = google_font("Nunito","400","400i","700"),
  text_font_google   = google_font("Nunito","400","400i","700","700i"),
  code_font_google   = google_font("Fira Mono"),
  header_h1_font_size = '2.50rem',
  header_h2_font_size = '1.25rem',
  header_h3_font_size = '1.00rem',
)

```


```{r, include=FALSE}
source("myclass-functions.R", local = knitr::knit_global())
```
$\newcommand\sem{\sigma_{\scriptscriptstyle \!M}}$
$\newcommand\sm{s_{\scriptscriptstyle M}}$
$\newcommand\smd{s_{\scriptscriptstyle M_D}}$
$\newcommand\tc{t_\text{crit}}$
$\newcommand\smm{s_{\scriptscriptstyle M_1-M_2}}$
$\newcommand\pv{s^2_p}$

## Introduction to Analysis of Variance
Previously we have seen that we can use a t-test to compare two means, e.g.,
to analyze data from experiments that test two conditions.
- e.g., To see if reading speed is different for Times versus Courier:
  - independent variable — __Typeface__: Times, Courier
  - dependent variable — __Reading speed__:  words per minute
  
- We can calculate
$$t=\frac{M_1-M_2}{\smm}$$
and find if the mean difference is significantly more than zero.

But what if the study has three, or four, or more conditions?